25 years of Social Work Research

### 2015-03-26 dataCleaning.Rmd
updated country stats

detach(package:stringi)
```

>>>>

detach(package:stringi)

setwd("C:/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
GDP<-read.csv("GDP.csv")
GDP<-select(GDP, Country=Country.Name, GDPperCapita=GDPperCapita2013, GDPRank)

PPP<-read.csv("PPP.csv")
PPP$PPP2013<-gsub(",", "", PPP$PPP2013)
PPP$PPP2013<-as.character(PPP$PPP2013)
PPP$PPP2013<-as.numeric(PPP$PPP2013)

articleCountries<-table(locations$record)
articleCountries<-as.data.frame(articleCountries)
articleCountries<-articleCountries%>%
                    select(Country=Var1, articleCount=Freq)

rankSet<-merge(articleCountries, GDP, by="Country", all=TRUE)
rankSet$articleCount[is.na(rankSet$articleCount)]<-0
rankSet<-merge(rankSet, PPP, by="Country", all=TRUE)

rankSet<-mutate(rankSet, articleRank=rank(-articleCount))
```
